\cvsection{Work Experience} % SECTION TITLE
\begin{cventries} % CONTENT
  \cvsimpleentry
    {\textbf{Viettel, Business Analyst}} % Job title
    {Vietnam, Aug. 2020 - Feb.2023} % Date
    {
      \begin{cvitems} % Description
        \item {Gathering, organising and analysing business data from various sources.}
        \item {Conducting market research to identify success factors and the latest trends.}
        \item {Defining and evaluating metrics for business profitability.}
        \item {Setting budgets for proposed business solutions.}
      \end{cvitems}
    }

  \cvsimpleentry
    {\textbf{Wilmar CLV - Calofic, Senior Procurement Staff}} % Job title
    {Vietnam, May. 2020 - Jul. 2020} % Date
    {
      \begin{cvitems} % Description
        \item {Understand, analyze, and evaluate procurement requirements for products.}
        \item {Research potential vendors.}
        \item {Maintain updated records of purchased products, delivery information and invoices.}
        \item {Review inventory and update as required.}
      \end{cvitems}
    }

  \cvsimpleentry
    {\textbf{Central Retail, Import - Logistics Trainee}} % Job title
    {Vietnam, Jan. 2020 - Apr. 2020} % Date
    {
      \begin{cvitems} % Description
        \item {Strictly follow the requirements of the management system, and input data into the computer system.}
        \item {Responsible for the transmission and classification of various documents and reports.}
        \item {Provide inventory information in a timely and accurate manner.}
      \end{cvitems}
    }

\end{cventries}
